The \dealii{} Library, Version 9.4

### 2022-06-01 9.4/paper.tex

Several classes have been added to the \texttt{NonMatching} namespace to enable the use of cut finite element methods, where the domain is immersed in the background mesh, as illustrated in Figure~\ref{fig:immersed-domain}.
Many of the new classes assume that the domain, $\Omega$, is described by a level set function,
$\psi : \mathbb{R}^d \to \mathbb{R}$, such that
\begin{align}
  \Omega = \{x \in \mathbb{R}^d : \psi(x)<0\},
  \qquad
  \Gamma = \partial \Omega = \{x \in \mathbb{R}^d : \psi(x) = 0\}.
\end{align}
\begin{itemize}
  \item The \texttt{MeshClassifier} class identifies how the active cells and faces are located relative to the zero contour of the level set function, as illustrated in Figure~\ref{fig:location-to-level-set}. Its \texttt{location\_to\_level\_set} function takes a cell/face and
        returns an enum, \texttt{ LocationToLevelSet}, which takes values \{\texttt{inside}, \texttt{outside}, \texttt{intersected}\}.
        These represent that $\psi$ is negative, positive, or varies in sign over the cell/face.
        That is, the cell/face is located inside/outside $\Omega$, or is intersected by $\Gamma$.
        This information is typically needed when choosing what element a cell of the \texttt{DoFHandler} should use.

@@

  \item \texttt{NonMatching::FEValues} combines the functionality of several of the above classes to simplify assembling. It works similarly to \texttt{hp::FEValues}.
  When calling the \texttt{reinit} function, the immersed quadrature rules are generated in the background and 
  \texttt{dealii::FEValues} objects for the inside/outside region and a \texttt{FEImmersedSurfaceValues} object for the surface regions are set up internally. These can then be obtained using getter-functions and used for the assembly.
  Since the generation of immersed quadrature rules is not for free,
  \texttt{NonMatching::FEValues} calls  \texttt{QuadratureGenerator} only if it is needed, i.e. if the cell is intersected. If the cell passed to \texttt{reinit} is not intersected, already cached \texttt{dealii::FEValues} objects will be returned by the getter functions.
  Correspondingly, the class \texttt{NonMatching::FEInterfaceValues} generates
  \texttt{dealii::FEInterfaceValues} objects for assembling face terms of the type $F \cap \{x : \psi(x) < 0 \}$ or $F \cap \{x : \psi(x) > 0 \}$.
\end{itemize}

>>>>

Several classes have been added to the \texttt{NonMatching} namespace to enable the use of cut finite element methods\cite{burman_cutfem_2015}.
In the literature, these types of methods are also referred to as immersed, extended, or fictitious finite element methods.
Here, the domain, $\Omega$, is immersed in the background mesh, as illustrated in Figure~\ref{fig:immersed-domain}.
Often, one solves for the degrees of freedom of the smallest submesh which completely covers the domain.
The bilinear form in the weak form can, for example, look like
\begin{equation}
  a(u,v) = (\nabla u, \nabla v)_\Omega - (\partial_n u, v)_\Gamma + \ldots
\end{equation}
Thus, when assembling, we are on each cell
required to integrate over the part of the domain and the part of the boundary, $\Gamma = \partial \Omega$, that falls inside the cell:
$K\cap \Omega$ and $K \cap \Gamma$.
Many of the new classes assume that the domain is described by a level set function,
$\psi : \mathbb{R}^d \to \mathbb{R}$, such that
\begin{align}
  \Omega = \{x \in \mathbb{R}^d : \psi(x)<0\},
  \qquad
  \Gamma = \{x \in \mathbb{R}^d : \psi(x) = 0\}.
\end{align}
\begin{itemize}
  \item The \texttt{MeshClassifier} class identifies how the active cells and faces are located relative to the zero contour of the level set function, as illustrated in Figure~\ref{fig:location-to-level-set}. Its \texttt{location\_to\_level\_set} function takes a cell/face and
        returns an enum, \texttt{ LocationToLevelSet}, which takes values \{\texttt{inside}, \texttt{outside}, \texttt{intersected}\}.
        These represent that $\psi$ is negative, positive, or varies in sign over the cell/face.
        That is, the cell/face is located inside/outside $\Omega$, or is intersected by $\Gamma$.
        This information is typically needed when choosing what element a cell of the \texttt{DoFHandler} should use.

@@

  \item \texttt{NonMatching::FEValues} combines the functionality of several of the above classes to simplify assembling. It works similarly to \texttt{hp::FEValues}.
  When calling the \texttt{reinit} function, the immersed quadrature rules are generated in the background and 
  \texttt{dealii::FEValues} objects for the inside/outside region and a \texttt{FEImmersedSurfaceValues} object for the surface regions are set up internally. These can then be obtained using getter-functions and used for the assembly.
  Since the generation of immersed quadrature rules is not for free,
  \texttt{NonMatching::FEValues} calls  \texttt{QuadratureGenerator} only if it is needed, i.e. if the cell is intersected. If the cell passed to \texttt{reinit} is not intersected, already cached \texttt{dealii::FEValues} objects will be returned by the getter functions.
  Correspondingly, the class \texttt{NonMatching::FEInterfaceValues} generates
  \texttt{dealii::FEInterfaceValues} objects for assembling face terms of the type $F \cap \{x : \psi(x) < 0 \}$ or $F \cap \{x : \psi(x) > 0 \}$.
\end{itemize}
The new \texttt{step-85} tutorial shows how many of these classes go together.
